The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-10 manuscript/paper.tex
added histogram figure and description to manuscript

>>>>

To visually compare 2023 baseball statistics versus those in 2022, two histograms
were created for each variable with 2023's data overlaid on 2022's. Figure~\ref{fig:Fig2}
illustrates an example of this for the Stolen Bases variable, as we think this
metric may be most affected by the rule changes, as stated previously. Both
histograms exhibit fairly similar distributions; however, in 2023, there is a
noticeable increase in the number of players with 20 or more stolen bases. This
observation supports our intuition that the rule changes contributed to an uptick
in this variable.

\begin{figure}[tbp]
  \centering
  \includegraphics{sb_hist}
  \caption{Comparison of Stolen Bases between the 2023 and 2022 MLB Seasons. The
  histograms illustrate the distribution of stolen base counts for players in each
  season, with blue representing 2023 and orange representing 2022.}
  \label{fig:Fig2}
\end{figure}
